What does the crowd believe?

### 2016-08-11 presentations/01_CogSci_2016/slides.Rmd
CogSci slides final make-over

# motivation

@@

<span style = "color:firebrick">New experimental measure</span>

- binned histogram task

@@

- infer population-level and subjective beliefs from data

@@

- belief + intention + rationality $\Rightarrow$ action

@@

@@

@@

## how to determine beliefs?

@@

@@

## slider ratings

@@

## number estimates

@@

## lightning round

@@

- do average BH ratings approximate latent population-level averages well?

@@

- take data from all three tasks
- infer latent subjective & "population-level beliefs"

@@

<span style = "color:firebrick">general</span>

- BH task averages are practical and reasonable approximations of the popuation-level central tendency of individual beliefs
- Bayesian data analysis is a great tool to extract information from multiple sources (e.g., data from different task types)

@@

<span style = "color:firebrick">specific</span>

- hierarchical modeling of population-level beliefs seems possible
- link functions for task choices seem reliable (enough)

>>>>

@@

<span style = "color:firebrick">new experimental measure</span>

- binned histogram task (Kao et al., 2014)

@@

- great tool to specify and test ideas about how unobservables (like beliefs) relate to each other and how they generate observable data

@@

- belief + desire + rationality $\Rightarrow$ action

@@

<span style = "color:firebrick">context</span>

Joe is an adult male from Texas. He went to a BBQ party yesterday.

@@

<!--

@@

-->
## how to determine beliefs?

@@

normalize slider rating by subject $\Rightarrow$ average over subjects $\Rightarrow$ <span style = "color:firebrick">BH task averages</span>

@@

## BH task averages

@@

## GAN frequencies

@@

## PC choice proportions

@@

- do BH task averages approximate the central tendency of beliefs in the population?

@@

- take data from all three tasks
- infer latent subjective & "population-level beliefs"
- specify "link functions"
    - how do subjective beliefs generate observable data

@@

- BH task averages are practical and reasonable approximations of the population-level central tendency of individual beliefs

@@

- Bayesian data analysis is a great tool to specify and test ideas about how unobservables (like beliefs) relate to each other and how they generate observable data
    - inferences based on diverse data from different tasks
